### 2021-04-29 Supplementary_Material/Global_Trait_Spectrum_Nectar.Rmd
figure missing values supp.

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

PC <- phyl_pca_forest
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

@@

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots

#Invert axes
PC$S[,1] <- -PC$S[,1]
PC$S[,2] <- -PC$S[,2]

@@

  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
    scale_alpha(guide = 'none')

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4)

@@

plot_grid(all_spp(PC))

>>>>

#Load data
phyl_pca_forest_nectar_all <- readRDS("Data/RData/phyl_pca_forest_nectar_all.rds")
dat_cleaning_5 <- readRDS("Data/RData/data_subset_nectar.rds")

PC <- phyl_pca_forest_nectar_all
#CHECK CONTENT
#EIGENVALUES
PC$Eval
#PC score (POINTS)
PC$S
#PC loadings (ARROWS)
PC$L

@@

@@

  dat$Nectar <- dat_cleaning_5$Nectar_presence_absence
  dat$Nectar[dat$Nectar=="yes"] <- "Presence"
  dat$Nectar[dat$Nectar=="no"] <- "Absence"
  # plot <- plot +geom_point(data=dat, aes(-x, -y, colour = density),size=0.65,shape = 1,colour = "black",alpha=0.8)

  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon',bins=8) + 
    scale_fill_continuous(low="green",high="red",guide=FALSE,lim=c(0.01,0.066),breaks = c(0.02, 0.035, 0.058), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.6),title="Kernel density"))+
    scale_alpha(guide = 'none')

@@

  plot <- plot + theme_bw()

  #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height", "Nectar" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(5,4.95,4.8,4.8,5.3,4.5,4.8)), y = -(PCAloadings$PC2*c(5.2,4.5,3.95,4.25,5,4.5,4.55)+c(0,0,0,0,0.2,0,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

@@

all_spp(PC)
